---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readwith

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/maurolepore/readwith.svg?branch=master)](https://travis-ci.org/maurolepore/readwith)
[![Coverage status](https://coveralls.io/repos/github/maurolepore/readwith/badge.svg)](https://coveralls.io/r/maurolepore/readwith?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/readwith)](https://cran.r-project.org/package=readwith)

__readwith__ allows you to read multiple files at once with any reading function. Its main function, `readwith::read_with()`, inputs a reader function and returns a modified version that reads any number of files and stores them into a list (provided the first argument of the reader function is a path to a file). Compared to other packages aimed to reading files, __readwith__ is simpler, more flexible, and has less dependencies.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/readwith")
```

## Example

```{r}
library(readwith)

readwith_example()

(csv_files <- readwith_example("csv"))
dir(csv_files)

csv_list <- read_with(read.csv)

csv_list(csv_files)

# Same
read_with(read.csv)(csv_files)
```

The argument `regexp` allows you to match specific files. You can pass arguments to the reader function via `...` (not an argument of `read_with()` but of the modified function it creates).

```{r}
(mixed_files <- readwith_example("mixed"))
dir(mixed_files)

# Using `regexp` to match .csv only
csv_list <- read_with(read.csv, regexp = "[.]csv$")

# Passing `stringsAsFactors` via the argument `...` of read.csv
result1 <- csv_list(mixed_files, stringsAsFactors = TRUE)
result2 <- csv_list(mixed_files, stringsAsFactors = FALSE)

# Compare
class(result1[["file1"]]$y)
class(result2[["file1"]]$y)

result2
```

You may use any available reader function, such as [`readr::read_csv()`](https://CRAN.R-project.org/package=readr), and  [`readxl::read_excel()`]( https://CRAN.R-project.org/package=readxl )), or create your own.

```{r}
read_rdata <- function(x) get(load(x))

(rdata_files <- readwith_example("rdata"))
dir(rdata_files)

read_with(read_rdata)(rdata_files)
```

# Related projects

There are great packages to read and write data, for example [__rio__](https://CRAN.R-project.org/package=rio) and [__io__](https://CRAN.R-project.org/package=io). Compared to them, this is how __readwith__ compares:

* __readwith__ may be confusing if you are unfamiliar with [function factories](https://adv-r.hadley.nz/function-factories.html). 
* __readwith__ is simpler:
    * It does not write data (only reads it).
    * It is not __readwith__ but the user who provides the reader function -- thus __readwith__ has almost no dependency.
* __readwith__ is more flexible because it works at a higher level of abstraction.
