---
title: "tor 1.0.0"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tor 1.0.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

install.packages(
  here::here(".buildignore/tor_1.0.0.zip"), 
  repos = NULL, type = "win.binary"
)
```

I'm happy to announce that __tor__ 1.0.0 in now on CRAN! 

__tor__ (to-R) helps you to
read multiple files from a single directory into R, as simply as possible. It makes a frequent task less painful. __tor__ is particularly useful during quick, exploratory data analysis and works well with the [tidyverse](https://www.tidyverse.org/). 

This initial release is minimal. It delivers the most useful functionality with few dependencies. Install the latest version of __tor__ from CRAN with:

```
install.packages("tor")
```

(Or [install the development version from GitHub](https://maurolepore.github.io/tor/index.html) which includes [exciting new features](https://maurolepore.github.io/tor/news/index.html).)

---

```{r}
library(tor)
```

All functions list whatever they read, and default to reading from the working directory.

`list_csv()` and friends import multiple files from a directory into a list.

```{r}
dir()

list_csv()
```

You may import specific files matching a pattern.

```{r}
(path_mixed <- tor_example("mixed"))
dir(path_mixed)

list_rdata(path_mixed, regexp = "[.]RData", ignore.case = FALSE)
```

`list_any()` is the most flexible function. You supply the function to read with.

```{r}
(path_csv <- tor_example("csv"))
dir(path_csv)

list_any(path_csv, readr::read_csv)
```

It understands lambda functions and formulas (powered by [__rlang__](https://rlang.r-lib.org/)).

```{r}
# Use the pipe (%>%)
library(magrittr)

(path_rdata <- tor_example("rdata"))
dir(path_rdata)

path_rdata %>% 
  list_any(function(x) get(load(x)))

# Same
path_rdata %>% 
  list_any(~get(load(.x)))
```

```{r, include=FALSE}
devtools::install_github("maurolepore/tor", upgrade = "never")
```

