---
title: "tor 1.0.0"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tor 1.0.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

I'm happy to announce that tor 1.0.0 in now on CRAN! __tor__ (to-R) helps you to
read multiple files from a single directory into R, as simply as possible. It makes a frequent task less painful. __tor__ is particularly useful during quick, exploratory data analysis and works well with the [tidyverse](https://www.tidyverse.org/). 

This initial release is minimal. It delivers the most useful functionality with few dependencies. Install the latest version of __tor__ from CRAN with:

```
install.packages("tor")
```

(The development version includes some [exciting new features](https://maurolepore.github.io/tor/news/index.html) and you can [install it from GitHub](https://maurolepore.github.io/tor/index.html).)

## Motivation

Your nickname is R-guru. Your colleague enjoys analyzing data and she head that R is great.

> I have a couple of minutes before the next meeting. Would you show me how to start playing with some data in R?

TWO MINUTES?! 

Don't panic. __tor__ is here to help you.

```{r}
# Here I have a bunch of files, including some .csv files with data.
dir()

# I "open" the programs I need to read the .csv files.
library(tor)

# And I list the data in all those .csv files
list_csv()

# Done.
```
